A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-06-04 manuscript.Rmd
run introduction through grammerly

Increasingly, scientists openly share their data, materials, and analysis code.
Sharing these digital artifacts increases scientific efficiency by enabling researchers to learn from each other, reuse materials, or review published research results.
However, making a research project reproducible comes with a variety of challenges and there is a dire need for standards of reproducibility.

This paper has two aims.
First, we want to introduce the reader to a workflow [see @Peikert2019 for details] that ensures reproducibility---defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code. 
The research community has long accepted reproducibility as integral to "good scientific practice", because empirical research hinges on its objectivity meaning "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper]
Often, however, projects can not be reproduced by other research teams, despite the best efforts by the creators.
We present four common threats to reproducibility and explain how we can address these with a combination of four solutions from the software engineering community.
Specifically, we demonstrate how the R package `repro` supports researchers in implementing this solution.
The second objective is to present an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the bulk of the manuscript, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.

[^popper]: In fact @popperLogicScientificDiscovery2002's famous criterion of demarcation is build around "inter-subjective testing", a concept which he later generalized to inter-subjective criticism (Footnote *¹, p. 22). Somewhat confusingly @popperLogicScientificDiscovery2002 uses the term "Reproducibility" for what we would call "Replication".

This tutorial is aimed at researchers who are willing to make code, data, and materials available and should help them to ensure reproducibility of relevant statistical results.
While the willingness to share materials is required for reproducing a project, it is not sufficient.
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and were able to reproduce the results of only 21 articles (within a reasonable period of time).

Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results.
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
To increase the proportion of reproducible projects, such reproducibility standard has to balance the trade-off between being rigorous and being easy to use.
A rigorous standard increases the likelihood of any individual project to be actually reproducible.
An easy to use standard on the other hand is more likely to be employed across many research projects.
The remainder of this paper is structured along these lines.
The first part introduces theoretical concepts and software solutions that together form a rigorous reproducibility standard.
The second part is a tutorial that shows how these software solutions can be easily employed by researchers with the help of the R package `repro`.

After introducing the conceptual building blocks, this tutorial guides the reader through each step of an open research project with an emphasis on guaranteeing reproducibility from the very first step on.
We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use a exemplary research question:

>>>>

Increasingly, scientists openly share their data, materials, and analysis code.
Sharing these digital artefacts increases scientific efficiency by enabling researchers to learn from each other, reuse materials, or review published research results.
However, making a research project reproducible comes with a variety of challenges, and there is a dire need for reproducibility standards.

This paper has two aims.
First, we want to introduce the reader to a workflow [see @Peikert2019 for details] that ensures reproducibility---defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code. 
The research community has long accepted reproducibility as integral to "good scientific practice" because empirical research hinges on its objectivity meaning "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper]
Often, however, projects can not be reproduced by other research teams, despite the best efforts by the creators.
We present four common threats to reproducibility and explain how we can address these with a combination of four solutions from the software engineering community.
Specifically, we demonstrate how the R package `repro` supports researchers in implementing this solution.
The second objective is to present an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the bulk of the manuscript, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.

[^popper]: In fact, @popperLogicScientificDiscovery2002's famous criterion of demarcation is built around "inter-subjective testing", a concept which he later generalised to inter-subjective criticism (Footnote *¹, p. 22). Somewhat confusingly, @popperLogicScientificDiscovery2002 uses the term "Reproducibility" for what we would call "Replication".

This tutorial aims at researchers who are willing to make code, data, and materials available and should help them ensure the reproducibility of relevant statistical results.
While the willingness to share materials is required for reproducing a project, it is not sufficient.
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).

Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results.
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
To increase the proportion of reproducible projects, such reproducibility standard has to balance the trade-off between being rigorous and being easy to use.
A rigorous standard increases the likelihood of any individual project to be actually reproducible.
An easy to use standard, on the other hand, is more likely to be employed across many research projects.
The remainder of this paper is structured along these lines.
The first part introduces theoretical concepts and software solutions that together form a rigorous reproducibility standard.
The second part is a tutorial that shows how these software solutions can be easily employed by researchers with the help of the R package `repro`.

After introducing the conceptual building blocks, this tutorial guides the reader through each step of an open research project, emphasising guaranteeing reproducibility from the very first step on.
We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:
